---
title: 'DDP: Course Project 1 - R Markdown & Leaflet'
author: "Cecilia Cruz-Ram, MD DPCOM"
date: "5/25/2020"
output:
  html_document:
    df_print: paged
geometry: margin = 0.5in
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Instructions

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Review Criteria

The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
2. Does the web page feature an interactive map that appears to have been created with Leaflet?

## Frankie's New York Buffalo Wings Locations

This page was built in RStudio using R Markdown and the Leaflet package to
build an interactive map of the locations of Frankie's New York Buffalo Wings.I love their Honey Mustard wings!

## Simulations:

A. Free Up Memory
```{r}
rm(list=ls())
```

B. Setwd
```{r}
setwd("~/Documents/Files/Zetch/Online Courses/Data Science Specialization Feb18/R/Developing Data Products")
```

C. Load Library
```{r}
library(leaflet)
```

D. Create Map
```{r}
fnyIcon <- makeIcon(
  iconUrl = "~/Documents/Files/Zetch/Online Courses/Data Science Specialization Feb18/R/Developing Data Products/Frankies.png",
  iconWidth = 30, iconHeight = 30,
  )

fnyLoc <- data.frame(name = c("Frankie's SM Megamall",
                              "Frankie's City Golf",
                              "Frankie's Kapitolyo",
                              "Frankie's Crossroads BGC"),
                     lat = c(14.583390, 14.588234, 14.574194, 14.553551), 
                     lng = c(121.056787, 121.067098, 121.060768, 121.051349))

fnySites <- c(
  "<a href='http://frankiesnywings.com/branches/sm-megamall/'>Frankie's New York Buffalo Wings SM Megamall</a>",
  "<a href='http://frankiesnywings.com/branches/city-golf/'>Frankie's New York Buffalo Wings City Golf Plaza</a>",
  "<a href='http://frankiesnywings.com/branches/kapitolyo/'>Frankie's New York Buffalo Wings Kapitolyo</a>",
  "<a href='http://frankiesnywings.com/branches/crossroad-bgc/'>Frankie's New York Buffalo Wings CrossRoads BGC</a>"
)

fnyLoc %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = fnyIcon, popup = fnySites)
```
